---
title: "Final Project"

toc: false
number-sections: true

format:
  docx:
    reference-doc: "./assets/sse-quarto-template.docx"

bibliography: assets/references.bib
csl: assets/apa-6th-edition.csl

editor: visual
---

```{r}
pckgs <- c("ggplot2", "ggfortify", "zoo", "forecast",
           "dynlm", "sandwich", "lmtest", "tseries",
           "plm", "plotly","rio")

pckgs <- pckgs[!pckgs %in% installed.packages()]

install.packages(pckgs,
                 dependencies = TRUE,
                 type = "binary")
```

```{r}
df <- rio::import("/Users/ThaoNghi/Documents/Data III/Final project/BE603_gr_6.xlsx")
```

# Hypotheses

We define the level of success as the degree to which the collected fund fulfill the initial goal:

```{r}
df$success_lv <- df$collected_funds/df$goal
```

*H1. There is a **positive and significant relationship** between **the success level of crowd-funding projects and the number of comments,** such that projects with higher comments count has higher level of success.*

*H2. Goal of fund is moderating the relationship between the success level of crowd-funding projects and the number of comments such that projects with higher goals often has higher level of success given the same comment counts.*

## General regression

```{r}
model_OLS <- lm(success_lv~
                + campaign_quality
                + goal
                + images
                + video
                + comments_count
                + updates_count
                + creators
                + business_venture
                + social
                + pitch_size
                + filler_words
                + duration
                + reach30in2
                + posemo
                + negemo
                + time,
                data = df)
summary(model_OLS)
```

```{r}
model_OLS_2 <- lm(success_lv~
+ goal
+ comments_count
+ pitch_size
+ reach30in2
+ posemo
+ time,
data = df)
summary(model_OLS_2)
```

## Moderating effect - comments_count:goal

```{r}
# Standardize varaibles
df$success_lv <- as.numeric(scale(as.numeric(df$success_lv)))
df$goal <- as.numeric(scale(as.numeric(df$goal)))
df$comments_count <- as.numeric(as.numeric(scale(df$comments_count)))
# Run the model
model_1 <- lm(success_lv ~ comments_count * goal, data = df)
# Display results
summary(model_1)
```
I think for the code below, we need to divide by sd(df$comments_count) to get the incremental effect
```{r}
quantiles <- quantile(df$goal, c(0.33, 0.67))
quantiles
low <- mean(df$goal[df$goal < -0.64])
medium <- mean(df$goal[df$goal >= -0.64 & df$goal < 0.16])
high <- mean(df$goal[df$goal>= 0.16])
df_prediction <- data.frame(goal = c(low, low, medium, medium, high, high),
comments_count = c(mean(df$comments_count),
                   mean(df$comments_count) + 1/sd(df$comments_count),
                   mean(df$comments_count),
                   mean(df$comments_count) + 1,
                   mean(df$comments_count),
                   mean(df$comments_count) + 1))
predictions <- predict(model_1, df_prediction, type = "response")
predictions
```
Then we'll see that the one unit increase in low and medium goals will lead to positive impact on the success level. But one unit increase in high goal will have counter-effect
(thats what i wrote from the seminar)
```{r}
# With point display
library(ggplot2)
df$goal <- "2 medium"  # Default
df$goal[df$goal < quantiles[1]] <- "1 low"
df$goal[df$goal > quantiles[2]] <- "3 high"
df$goal <- factor(df$goal, levels = c("1 low", "2 medium", "3 high"))

ggplot(df) +
aes(y = success_lv, x = comments_count, color = as.factor(goal)) +
geom_smooth(method = "lm", se = FALSE) +
labs(y = "success_lv",
x = "comments_count",
color = "goal") + theme_classic()
```
the graph does not work, maybe try this one. But this one suggests that ther is NO MODERATING EFFECT
```
{r}
library(ggplot2)

# Create a new column for labeling goal levels
df_prediction$goal_level <- factor(
  df_prediction$goal_std, 
  labels = c("Low Goal", "Medium Goal", "High Goal")
)

# Plot the interaction
ggplot(df_prediction, aes(x = comments_count_std, y = predictions, color = goal_level)) +
  geom_line(size = 1) +  # Add lines for each goal level
  geom_point(size = 2) +  # Add points for clarity
  labs(
    title = "Interaction Plot",
    x = "Comments (Standardized)",
    y = "Predicted Success Level (Standardized)",
    color = "Goal Level"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )
```

## Moderating effect - reach30in2:goal

```{r}
df2 <- rio::import("/Users/ThaoNghi/Documents/Data III/Final project/BE603_gr_6.xlsx")
df2$success_lv <- df2$collected_funds/df2$goal
```

```{r}
# Run the model
model_2 <- lm(success_lv ~ reach30in2 * goal, data = df2)
# Display results
summary(model_2)
```
