---
title: "Final Project"

toc: false
number-sections: true

format:
  docx:
    reference-doc: "./assets/sse-quarto-template.docx"

bibliography: assets/references.bib
csl: assets/apa-6th-edition.csl

editor: visual
---

```{r}
pckgs <- c("ggplot2", "ggfortify", "zoo", "forecast",
           "dynlm", "sandwich", "lmtest", "tseries",
           "plm", "plotly","rio")

pckgs <- pckgs[!pckgs %in% installed.packages()]

install.packages(pckgs,
                 dependencies = TRUE,
                 type = "binary")
```

```{r}
df <- rio::import("/Users/ThaoNghi/Documents/Data III/Final project/BE603_gr_6.xlsx")
```

# Hypotheses

We define the level of success as the degree to which the collected fund fulfill the initial goal:

```{r}
df$success_lv <- df$collected_funds/df$goal
```

*H1. There is a **positive and significant relationship** between **the success level of crowd-funding projects and the number of comments,** such that projects with higher comments count has higher level of success.*

*H2. Goal of fund is moderating the relationship between the success level of crowd-funding projects and the number of comments such that projects with higher goals often has higher level of success given the same comment counts.*

## General regression

```{r}
model_OLS <- lm(success_lv~
                + campaign_quality
                + goal
                + images
                + video
                + comments_count
                + updates_count
                + creators
                + business_venture
                + social
                + pitch_size
                + filler_words
                + duration
                + reach30in2
                + posemo
                + negemo
                + time,
                data = df)
summary(model_OLS)
```

```{r}
model_OLS_2 <- lm(success_lv~
+ goal
+ comments_count
+ pitch_size
+ reach30in2
+ posemo
+ time,
data = df)
summary(model_OLS_2)
```

## Moderating effect - comments_count:goal

```{r}
# Standardize varaibles
df$success_lv <- as.numeric(scale(as.numeric(df$success_lv)))
df$goal <- as.numeric(scale(as.numeric(df$goal)))
df$comments_count <- as.numeric(as.numeric(scale(df$comments_count)))
# Run the model
model_1 <- lm(success_lv ~ comments_count * goal, data = df)
# Display results
summary(model_1)
```

```{r}
quantiles <- quantile(df$goal, c(0.33, 0.67))
quantiles
low <- mean(df$goal[df$goal < -0.64])
medium <- mean(df$goal[df$goal >= -0.64 & df$goal < 0.16])
high <- mean(df$goal[df$goal>= 0.16])
df_prediction <- data.frame(goal = c(low, low, medium, medium, high, high),
comments_count = c(mean(df$comments_count),
                   mean(df$comments_count) + 1,
                   mean(df$comments_count),
                   mean(df$comments_count) + 1,
                   mean(df$comments_count),
                   mean(df$comments_count) + 1))
predictions <- predict(model_1, df_prediction, type = "response")
predictions
```

```{r}
# With point display
library(ggplot2)
df$goal <- "2 medium"  # Default
df$goal[df$goal < quantiles[1]] <- "1 low"
df$goal[df$goal > quantiles[2]] <- "3 high"
df$goal <- factor(df$goal, levels = c("1 low", "2 medium", "3 high"))

ggplot(df) +
aes(y = success_lv, x = comments_count, color = as.factor(goal)) +
geom_smooth(method = "lm", se = FALSE) +
labs(y = "success_lv",
x = "comments_count",
color = "goal") + theme_classic()
```

## Moderating effect - reach30in2:goal

```{r}
df2 <- rio::import("/Users/ThaoNghi/Documents/Data III/Final project/BE603_gr_6.xlsx")
df2$success_lv <- df2$collected_funds/df2$goal
```

```{r}
# Run the model
model_2 <- lm(success_lv ~ reach30in2 * goal, data = df2)
# Display results
summary(model_2)
```
